The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-25 paper/Analisis.tex
minor changes in conclusions

As first we see how the width of the line changes using a modified FWHM
explained in section \ref{sec:widthpeak}, and we found that as gas bulk 
rotation increase also the width increase in a factor of $2-3$ in comparison 
with the static case. We also take into account the influence of the observer 
viewing angle, we found that observers with a line of sight perpendicular  
to the axis of rotation measure a $15\%$ larger line width than those 
aligned with the rotation axis.

As many observational spectra Ly$\alpha$ emission line (Kulas et al)
is double  peaked, these peaks provide important information
concerning gas kinematics and geometry,  which can be partially
explained with inflows/outflows of gas content.  We study the effect
of rotation in the position of this peaks, and we find  that the
position of the maxima does change with rotation for the homogeneous
models when the double peak merged into a single peak as velocity
increase. This effect is not seen for the central distribution when
the double peak  remains constant as the velocity increase. We also
find that there is no dependency in the observer viewing angle with
the maxima position.

@@

As an application of these results we compute the integrated flux
taking into account the narrow band filters used by (Steidel et al
2011), for our models we found an important decrease up to $~40\%$ for
the homogeneous models, and up to $22\%$ for the dusty homogeneous
models in the flux as velocity increase.  Also we calculate at what
redshift should the filter be in order to get the maximum  flux, and
for the tree filters we get values that rely in the filter redshift
range. This effects would have a relevant implication at the time to
find high redshift galaxies.

>>>>

As first we see how the width of the line changes using a modified FWHM
explained in section \ref{sec:widthpeak}, and we found that as gas bulk 
rotation increase also the width increase in a factor of $2-3$ in comparison 
with the static case. 'We also take into account the influence of the observer 
viewing angle, we found that observers with a line of sight perpendicular  
to the axis of rotation measure a $15\%$ larger line width than those 
aligned with the rotation axis.'

As many observational spectra Ly$\alpha$ emission line (Kulas et al, Yamada et al)
is double  peaked, these peaks provide important information
concerning gas kinematics and geometry,  which can be partially
explained with inflows/outflows of gas content.  We study the effect
of rotation in the position of this peaks, and we find  that the
position of the maxima does change with rotation for the homogeneous
models when the double peak merged into a single peak as velocity
increase. This effect is not seen for the central distribution when
the double peak  remains constant as the velocity increase. We also
find that there is no dependency in the observer viewing angle with
the maxima position.

@@

%As an application of these results we compute the integrated flux
%taking into account the narrow band filters used by (Steidel et al
%2011), for our models we found an important decrease up to $~40\%$ for
%the homogeneous models, and up to $22\%$ for the dusty homogeneous
%models in the flux as velocity increase.  Also we calculate at what
%redshift should the filter be in order to get the maximum  flux, and
%for the tree filters we get values that rely in the filter redshift
%range. This effects would have a relevant implication at the time to
%find high redshift galaxies.
